Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-06-04 pldi14/sec-concl.tex
Revise PLDI'14 conclusion

\section{Chapter conclusion}
\label{ssec:future}
In this chapter we have presented \ILC, an approach to lifting incremental computations
on first-order programs to incremental computations on higher-order
programs. We have presented a machine-checked correctness proof 
of a formalization of \ILC\ and an initial experimental evaluation
in the form of an implementation, a sample plugin for maps and bags,
and a non-trivial example that was incrementalized successfully and
efficiently.

>>>>

\chapter{Conclusion}
\label{ssec:future}
In this part we have presented \ILC, an approach to lifting incremental computations
on first-order programs to incremental computations on higher-order
programs. We have presented a machine-checked correctness proof 
of a formalization of \ILC\ and an initial experimental evaluation
in the form of an implementation, a sample plugin for maps and bags,
and a non-trivial example that was incrementalized successfully and
efficiently.
